---
title: "Getting Started"
author: "Jay Achar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```

# Accessing instructions
This instruction vignette is available either online at **[Github](https://github.com/JayAchar/tbreportr)** or through **[emailing the author](mailto:jay.achar@london.msf.org?subject=tbreportr instructions)**. Alternatively, you may ask your medical manager since they may also have a copy. For the most up to date version, it's recommended to visit the online repository linked. 

# Purpose

This R package, `tbcleanr`, has been developed to support MSF field staff using either Koch 6 or EpiInfo to clean routinely collected programme TB data. Currently, the package will only accept admission data sets, but laboratory and change drug data sets will likely be accepted in future versions. Reported bugs or requested new features will be incorporated as time allows. 

# How to

To use this package, R experience is required. Future packages, such as `tbreportr` will allow automated report generation. 

After reading in the admission data export from either Koch 6 or EpiInfo, install and load the `tbcleanr` package. 

``` {r install}
library(devtools)
install_github("JayAchar/tbcleanr")
library(tbcleanr)
```

A single function can be called to simplify admission data cleaning:

``` {r clean}
x <- adm_data_cleanr(x)
```

Where necessary, additional variables can be included for subsetting and manual cleaning:

``` {r addition}
x <- adm_data_cleanr(x, add = "REGRP")

```

Further function-specific documentation are available within the package. 
# Future developments

Functionality will be added for laboratory and change drug data sets. In parallel, `tbgeneratr` and `tbreportr` are being developed to firstly generate new varialbe such as culture conversion time, and secondly to automate cohort reporting for programme evaluation purposes. 

